Industrial, large-scale model predictive control with structured neural networks

### 2021-02-11 paper.tex
minor updates.

We now present the robustness properties of NN controllers. The optimal MPC
controller designed for a nominal linear system ignoring disturbances is known
to be inherently robust to bounded state estimation errors and disturbances
\citep*{heath:wills:2005, pannocchia:rawlings:wright:2011}. The approximation
error of the MPC feedback law by a NN can be viewed as an additional
disturbance, and the existing input-to-state stability results
\citep*{sontag:wang:1995} are used to establish the allowable approximation
error in the NN for the NN controller to be robust to disturbances. Theorem
\ref{thm:nnrobustness} states this allowable approximation error and specifies
the size of disturbances for which the NN controller is robust.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth,
                     height=0.22\textheight]{cstrs_with_flash.pdf}
    \caption{Schematic of the CSTRs with a flash separator model.}
    \label{fig:schematic_cstrs}
\end{figure}

@@

\begin{figure*}[!h]
    \includegraphics[page=31, width=0.5\textwidth,
        height=0.28\textheight]{cstrs_comparision_plots.pdf} \hfill
        \includegraphics[page=34, width=0.5\textwidth,
        height=0.28\textheight]{cstrs_comparision_plots.pdf} \vfill
    \vspace{-0.1in}
    \begin{center}\includegraphics[page=33, width=0.5\textwidth,
        height=0.28\textheight]{cstrs_comparision_plots.pdf}
    \end{center}
    \vspace{-0.2in}
    \caption{Simulation statistics for the  
    CSTRs with a flash separator example. Data requirement to obtain accurate NN
    controllers (top left), online computation times of the NNs and MPC
    controller (top right), and the controller performance index obtained with
    the NNs, SS, satK and MPC controllers (center bottom).The performance of the
    three NN and optimal MPC controllers are indistinguishable.}	
    \label{fig:cstrs_statistics}
\end{figure*}

@@

\begin{figure*}[!h]
    \includegraphics[page=41, width=0.5\textwidth,
        height=0.28\textheight]{cdu_comparision_plots.pdf} \hfill
        \includegraphics[page=43, width=0.5\textwidth,
        height=0.28\textheight]{cdu_comparision_plots.pdf} \vfill
    \vspace{-0.1in}
    \begin{center}\includegraphics[page=42, width=0.5\textwidth,
        height=0.28\textheight]{cdu_comparision_plots.pdf}\end{center}
    \vspace{-0.2in}
    \caption{Simulation statistics for the industrial crude distillation unit
    example. Data requirement to obtain accurate NN controllers (top left),
    online computation times of the NNs and MPC controller (top right), and the
    controller performance index obtained with the NNs, satK and MPC controllers
    (center bottom). The performance of the three NN and optimal MPC controllers
    are indistinguishable.}	
    \label{fig:cdu_statistics}
\end{figure*}

>>>>

We now present the robustness properties of NN controllers. The optimal MPC
controller designed for a nominal linear system ignoring disturbances is known
to be inherently robust to bounded state estimation errors and disturbances
\citep*{heath:wills:2005, pannocchia:rawlings:wright:2011}. The approximation
error of the MPC feedback law by a NN can be viewed as an additional
disturbance, and the existing input-to-state stability results
\citep*{sontag:wang:1995} are used to establish the allowable approximation
error in the NN for the NN controller to be robust to disturbances. Theorem
\ref{thm:nnrobustness} states this allowable approximation error and specifies
the size of disturbances for which the NN controller is robust. This result also
holds for other approximate MPC controllers, which use different parametric
functions to approximate the optimal control law such as polynomials and other
piecewise affine functions.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth,
                     height=0.25\textheight]{cstrs_with_flash.pdf}
    \caption{Schematic of the CSTRs with a flash separator model.}
    \label{fig:schematic_cstrs}
\end{figure}

@@

\begin{figure*}[!h]
    \includegraphics[page=31, width=0.5\textwidth,
        height=0.27\textheight]{cstrs_comparision_plots.pdf} \hfill
        \includegraphics[page=34, width=0.5\textwidth,
        height=0.27\textheight]{cstrs_comparision_plots.pdf} \vfill
    \vspace{-0.1in}
    \begin{center}\includegraphics[page=33, width=0.5\textwidth,
        height=0.27\textheight]{cstrs_comparision_plots.pdf}
    \end{center}
    \vspace{-0.2in}
    \caption{Simulation statistics for the  
    CSTRs with a flash separator example. Data requirement to obtain accurate NN
    controllers (top left), online computation times of the NNs and MPC
    controller (top right), and the controller performance index obtained with
    the NNs, SS, satK and MPC controllers (center bottom).The performance of the
    three NN and optimal MPC controllers are indistinguishable.}	
    \label{fig:cstrs_statistics}
\end{figure*}

@@

\begin{figure*}[!h]
    \includegraphics[page=41, width=0.5\textwidth,
        height=0.27\textheight]{cdu_comparision_plots.pdf} \hfill
        \includegraphics[page=43, width=0.5\textwidth,
        height=0.27\textheight]{cdu_comparision_plots.pdf} \vfill
    \vspace{-0.1in}
    \begin{center}\includegraphics[page=42, width=0.5\textwidth,
        height=0.27\textheight]{cdu_comparision_plots.pdf}\end{center}
    \vspace{-0.2in}
    \caption{Simulation statistics for the industrial crude distillation unit
    example. Data requirement to obtain accurate NN controllers (top left),
    online computation times of the NNs and MPC controller (top right), and the
    controller performance index obtained with the NNs, satK and MPC controllers
    (center bottom). The performance of the three NN and optimal MPC controllers
    are indistinguishable.}	
    \label{fig:cdu_statistics}
\end{figure*}
